\documentclass[a4paper]{article}
% \usepackage[margin=1.25in]{geometry}
\usepackage[inner=2.0cm,outer=2.0cm,top=2.5cm,bottom=2.5cm]{geometry}
% \usepackage{ctex}
\usepackage{color}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{enumerate}

\newcommand{\homework}[5]{
    \pagestyle{myheadings}
    \thispagestyle{plain}
    \newpage
    \setcounter{page}{1}
    \noindent
    \begin{center}
    \framebox{
        \vbox{\vspace{2mm}
        \hbox to 6.28in { {\bf Optimization Methods \hfill #2} }
        \vspace{6mm}
        \hbox to 6.28in { {\Large \hfill #1 \hfill} }
        \vspace{6mm}
        \hbox to 6.28in { {\it Instructor: {\rm #3} \hfill Name: {\rm #4}, StudentId: {\rm #5}}}
        \vspace{2mm}}
    }
    \end{center}
    % \markboth{#4 -- #1}{#4 -- #1}
    \vspace*{4mm}
}


\newenvironment{solution}
{\color{blue} \paragraph{Solution.}}
{\newline \qed}

\begin{document}
%==========================Put your name and id here==========================
\homework{Homework 3}{Fall 2019}{Lijun Zhang}{Student name}{Student id}

\paragraph{Notice}
\begin{itemize}
    \item The submission email is: \textbf{njuoptfall2019@163.com}.
    \item Please use the provided \LaTeX{} file as a template. If you are not familiar with \LaTeX{}, you can also use Word to generate a \textbf{PDF} file.
\end{itemize}
\paragraph{Problem 1: Equality Constrained Least-squares}
~\\
Consider the equality constrained least-squares problem
\begin{gather*}
\begin{matrix}
\text{minimize~~} & \frac{1}{2}\|Ax-b\|_2^2\\
\text{subject to} & Gx=h~~\\
\end{matrix}
\end{gather*}
where $A\in\mathbf{R}^{m\times n}$ with $\mathbf{rank}~A=n$, and $G\in\mathbf{R}^{p\times n}$ with $\mathbf{rank}~G=p$.
\begin{enumerate}[a)]
    \item Derive the Lagrange dual problem with Lagrange multiplier vector $v$.
    \item Derive expressions for the primal solution $x^\star$ and the dual solution $v^\star$.
\end{enumerate}
\begin{solution}
Write your solution here.
\end{solution}

\paragraph{Problem 2: Support Vector Machines}
~\\
Consider the following optimization problem
\begin{gather*}
\begin{matrix}
\text{minimize~~} & \sum_{i=1}^n\max\left(0,1-y_i(w^Tx_i+b)\right)+\frac{\lambda}{2}\|w\|_2^2\\
\end{matrix}
\end{gather*}
where $x_i\in\mathbf{R}^{d},y_i\in \mathbf{R},i=1,\cdots,n$ are given, and $w\in \mathbf{R}^d,b\in\mathbf{R}$ are the variables.
\begin{enumerate}[a)]
    \item Derive an equivalent problem by introducing new variables $u_i,i=1,\cdots,n$ and equality constraints \[u_i=y_i(w^Tx_i+b),i=1,\cdots,n.\]
    \item Derive the Lagrange dual problem of the above equivalent problem.
    \item Give the Karush-Kuhn-Tucker conditions.
\end{enumerate}

\noindent\emph{Hint: Let $\ell(x)=\max(0,1-x)$. Its conjugate function $\ell^\ast(y)=\sup\limits_{x}(yx-\ell(x))=\left\{
\begin{aligned}
&y, \quad-1\leq y\leq0 \\
&\infty,\quad\text{otherwise}
\end{aligned}
\right.$}
\begin{solution}
Write your solution here.
\end{solution}

\paragraph{Problem 3: Euclidean Projection onto the Simplex}
~\\
Consider the following optimization problem
\begin{gather*}
\begin{matrix}
\text{minimize~~} & \frac{1}{2}\left\|y-x\right\|^2_2\quad\\
\text{subject to} & \mathbf{1}^Ty=r\quad\quad\\
&y\succeq0\quad\quad\quad
\end{matrix}
\end{gather*}
where $r>0$, $x\in \mathbb{R}^n$ is given, and $y\in \mathbf{R}^n$ is the variable. Give an algorithm to solve this problem and prove the correctness of your algorithm.

\noindent\emph{Hint: Derive the Lagrangian of this problem and apply the Karush-Kuhn-Tucker conditions. If you need more hints, please read the following paper \cite{Wang2013}}
\begin{solution}
Write your solution here.
\end{solution}

\paragraph{Problem 4: Optimality Conditions}
~\\
Consider the problem
\begin{equation*}
    \begin{split}
        &\text{minimize~~} \quad  \text{tr}(2X) - \log{\det{(3X)}} \\
        &\text{subject to} \quad~  2Xs=y
    \end{split}
\end{equation*}
with variable $X \in \mathbf{S}^n$ and domain $\mathbf{S}_{++}^n$. Here, $y \in \mathbf{R}^n$ and $s \in \mathbf{R}^n$ are given, with $s^T y =1$.
\begin{enumerate}[a)]
    \item Give the Lagrange and then derive the Karush-Kuhn-Tucker conditions.
    \item Verify that the optimal solution is given by
    \begin{equation*}
        X^\star = \frac{1}{2} \left(I + yy^T - \frac{ss^T}{s^T s}\right) .
    \end{equation*}
\end{enumerate}

\begin{solution}
Write your solution here.
\end{solution}


\begin{thebibliography}{1}

\bibitem{Wang2013}
Weiran Wang, and Miguel \'{A}. Carreira-Peroi\~{n}\'{a}n.
\newblock Projection onto the probability simplex: An efficient algorithm with a simple proof, and an application.
\newblock \emph{arXiv:1309.1541}, 2013.

\end{thebibliography}

\end{document}
